---
title: "Predict Property"
author: "Quang Trung"
date: "March 31, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
setwd("C:/Users/DoQuangTrung/Desktop/project")
data <- read.csv("build_mode.csv")
library(dplyr)
library(tidyverse)
library(psych)
library(grid)
library(ggplot2)

data$MSSubClass  <- factor(data$MSSubClass)
data$OverallQual <- factor(data$OverallQual)
data$OverallCond <- factor(data$OverallCond) 
data$FullBath <-factor(data$FullBath)
data$BsmtFullBath <- factor(data$BsmtFullBath)
data$FullBath <-factor(data$FullBath)
data$HalfBath <- factor(data$HalfBath)
data$BedroomAbvGr <- factor(data$BedroomAbvGr)
data$KitchenAbvGr <- factor(data$KitchenAbvGr)
data$TotRmsAbvGrd <- factor(data$TotRmsAbvGrd)
data$Fireplaces <- factor(data$Fireplaces)
data$GarageCars <-factor(data$GarageCars)
# data$MoSold<-factor(data$MoSold)
# data$YearBuilt<-factor(data$YearBuilt)
# data$YearRemodAdd<-factor(data$YearRemodAdd)

attach(data)
```

# REAL ESTATE
this is a report, prediction'Property.
Dataset: kaggle.

*[hello]

###Problem : Using several of feature to predict sale price

### Description of features 

MSSubClass: Identifies the type of dwelling involved in the sale.	

        20	1-STORY 1946 & NEWER ALL STYLES
        30	1-STORY 1945 & OLDER
        40	1-STORY W/FINISHED ATTIC ALL AGES
        45	1-1/2 STORY - UNFINISHED ALL AGES
        50	1-1/2 STORY FINISHED ALL AGES
        60	2-STORY 1946 & NEWER
        70	2-STORY 1945 & OLDER
        75	2-1/2 STORY ALL AGES
        80	SPLIT OR MULTI-LEVEL
        85	SPLIT FOYER
        90	DUPLEX - ALL STYLES AND AGES
       120	1-STORY PUD (Planned Unit Development) - 1946 & NEWER
       150	1-1/2 STORY PUD - ALL AGES
       160	2-STORY PUD - 1946 & NEWER
       180	PUD - MULTILEVEL - INCL SPLIT LEV/FOYER
       190	2 FAMILY CONVERSION - ALL STYLES AND AGES

LotFrontage: Linear feet of street connected to property

LotArea: Lot size in square feet

OverallQual: Rates the overall material and finish of the house

       10	Very Excellent
       9	Excellent
       8	Very Good
       7	Good
       6	Above Average
       5	Average
       4	Below Average
       3	Fair
       2	Poor
       1	Very Poor
	
OverallCond: Rates the overall condition of the house

       10	Very Excellent
       9	Excellent
       8	Very Good
       7	Good
       6	Above Average	
       5	Average
       4	Below Average	
       3	Fair
       2	Poor
       1	Very Poor
		
YearBuilt: Original construction date

YearRemodAdd: Remodel date (same as construction date if no remodeling or additions)

MasVnrArea: Masonry veneer area in square feet

BsmtFinType1: Rating of basement finished area

       GLQ	Good Living Quarters
       ALQ	Average Living Quarters
       BLQ	Below Average Living Quarters	
       Rec	Average Rec Room
       LwQ	Low Quality
       Unf	Unfinshed
       NA	No Basement
		
BsmtFinSF1: Type 1 finished square feet

BsmtFinType2: Rating of basement finished area (if multiple types)

       GLQ	Good Living Quarters
       ALQ	Average Living Quarters
       BLQ	Below Average Living Quarters	
       Rec	Average Rec Room
       LwQ	Low Quality
       Unf	Unfinshed
       NA	No Basement

BsmtFinSF2: Type 2 finished square feet

BsmtUnfSF: Unfinished square feet of basement area

TotalBsmtSF: Total square feet of basement area

1stFlrSF: First Floor square feet
 
2ndFlrSF: Second floor square feet

LowQualFinSF: Low quality finished square feet (all floors)

GrLivArea: Above grade (ground) living area square feet

BsmtFullBath: Basement full bathrooms

BsmtHalfBath: Basement half bathrooms

FullBath: Full bathrooms above grade

HalfBath: Half baths above grade

Bedroom: Bedrooms above grade (does NOT include basement bedrooms)

Kitchen: Kitchens above grade

TotRmsAbvGrd: Total rooms above grade (does not include bathrooms)

GarageYrBlt: Year garage was built

GarageCars: Size of garage in car capacity

GarageArea: Size of garage in square feet

WoodDeckSF: Wood deck area in square feet

OpenPorchSF: Open porch area in square feet

EnclosedPorch: Enclosed porch area in square feet

3SsnPorch: Three season porch area in square feet

ScreenPorch: Screen porch area in square feet

PoolArea: Pool area in square feet

DMoSold: Month Sold (MM)

YrSold: Year Sold (YYYY)


##Descriptive statistics 


####  OutCome variable :SalePrice


```{r saleprice , echo= FALSE}

box<- ggplot(data,aes(x='', y=SalePrice) ) + geom_boxplot(fill="maroon" , notch = T, notchwidth = 0.1)+
  theme_bw() +
  theme( panel.grid.major = element_blank(), panel.grid.minor = element_blank())
summary(SalePrice)

de<-ggplot(data,aes(SalePrice) ) + geom_density(fill="maroon" )+
  theme_bw() +
  theme( panel.grid.major = element_blank(), panel.grid.minor = element_blank())



pushViewport(viewport(layout = grid.layout(1, 2)))
print(box, vp = viewport(layout.pos.row = 1, layout.pos.col = 1))
print(de, vp = viewport(layout.pos.row = 1, layout.pos.col = 2))

```
```
The distribution  of Sale Price seem like normal distribution
```

### Detail Feature

####1:MSSubClass

```{r MSSubClass , echo=FALSE}

ggplot(data, aes(x = "", y="", fill = MSSubClass)) + 
  geom_bar(width = 1, stat = "identity") +
  #theme(axis.line = element_blank(), 
  #    plot.title = element_text(hjust=0.5)) + 
  
  labs(fill="class", 
       x=NULL, 
       y=NULL, 
       title="Pie Chart of MSSubClass",
       caption="Identifies the type of dwelling involved in the sale."
  )+ coord_polar(theta = "y", start=0)

summary(MSSubClass)


```

So we see :  type 20 (536 obs), type 60  (299 obs) and type 50 (144 obs)  are  favor type.


####2:LotFrontage

Linear feet of street connected to property

```{r LotFrontage , echo=FALSE}
boxplot(LotFrontage , main =" Plot box LotFrontAge", col="maroon" )

summary(LotFrontage)
vars=cbind(LotFrontage,SalePrice)
# pairs.panels(vars)# tạo ma trận tương quan
corr.test(vars)
```

``` 
The mean of LotFrontage is 70.05 . 
Confidence interval ( 95% ) from 59.00 to 80
lotfrontage has 259 missing value
the correlation between  LotFrontage and saleprice is 0.35  
  
```



####3:LotArea 
Lot size in square feet


```{r LotArea , echo=FALSE}

ggplot(data,aes(LotArea)) + geom_density(fill='maroon')+ theme_bw()
summary(LotArea)
corr.test(cbind(LotArea,SalePrice))

```

The correlation between  LotFrontage and saleprice :0.26
The Confidence interval : [7554 , 11602]




####5-6 : OverallQual ,OverallCond.

OverallQual: Rates the overall material and finish of the house .

OverallCond: Rates the overall condition of the house

```
       10	Very Excellent
       9	Excellent
       8	Very Good
       7	Good
       6	Above Average
       5	Average
       4	Below Average
       3	Fair
       2	Poor
       1	Very Poor
```

```{r overall , echo=FALSE}

plot1<-ggplot(data,aes(OverallQual)) + geom_bar(fill ='maroon') + 
  theme_bw() +
  theme( panel.grid.major = element_blank(), panel.grid.minor = element_blank())+
  labs(
    subtitle = " Rates the overall\n material and finish of the house ",
    title=" Distribution \nof OverAll Quaity",
    y= "Counts",
    x="rate"
  )

plot2<-ggplot(data,aes(OverallCond)) + geom_bar(fill ='maroon') + 
  theme_bw() +
  theme( panel.grid.major = element_blank(), panel.grid.minor = element_blank())+
  labs(
    subtitle = " Rates the overall \ncondition of the house ",
    title="Distribution \n OverAll OverallCond ",
    y= "Counts",
    x="rates"
  )

pushViewport(viewport(layout = grid.layout(1, 3)))
print(plot1, vp = viewport(layout.pos.row = 1, layout.pos.col = 1))
print(plot2, vp = viewport(layout.pos.row = 1, layout.pos.col = 3))


```

From plot. We see rates  5 6 7 the mostly


#### 7-8 : YearBuilt and YearRemodAdd

YearBuilt: Original construction date

YearRemodAdd: Remodel date (same as construction date if no remodeling or additions)



```{r yearbuil , echo= FALSE}


ybplot<-ggplot(data,aes(YearBuilt))+ geom_bar(fill ='maroon')+theme_bw() +
  theme( panel.grid.major = element_blank(), panel.grid.minor = element_blank())+
  labs(
    subtitle = " Original construction year ",
    title=" YearBuid  ",
    y= "",
    x="Year"
  )

yraplot<-ggplot(data,aes(YearRemodAdd))+ geom_bar(fill ='maroon')+theme_bw() +
  theme( panel.grid.major = element_blank(), panel.grid.minor = element_blank())+
  labs(
    subtitle = " Remodel date \n(same as construction date \nif no  remodeling or additions) ",
    title="   YearRemodAdd  ",
    y= "",
    x="Year"
  )
# sẽ để song song
pushViewport(viewport(layout = grid.layout(1, 2)))

print(ybplot, vp = viewport(layout.pos.row = 1, layout.pos.col = 1))
print(yraplot, vp = viewport(layout.pos.row = 1, layout.pos.col = 2))

print('YearBuilt summary')
summary(YearBuilt)

print("YearRemodAdd summary")
summary(YearRemodAdd)

```

#### 9 - 10 :YrSold and MoSold 

YrSold : Month Sold

MoSold : Year Sold

```{r mysold , echo=F }

ggplot(data,aes(YrSold))+ geom_bar(aes(fill=factor(MoSold)),position="dodge" )+
  
  theme_bw() + theme( panel.grid.major = element_blank(), panel.grid.minor = element_blank())+
  labs(
    title=" Month n Year Sold  ",
    subtitle = " month group Year Sold ",
    fill="Month",
    y= "Count",
    x="Year"
  )
```

Insight : Summer is the best time for sale 



####11 :GarageYrBlt
GarageYrBlt  Year garage was built 


```{r GarageYrBlt, echo=F, message=FALSE, warning=FALSE}
ggplot(data,aes(GarageYrBlt))+ geom_histogram(fill ='maroon' )+
  
  theme_bw() + theme( panel.grid.major = element_blank(), panel.grid.minor = element_blank())+
  labs(
    title=" GarageYrBlt  ",
    subtitle = " the Year when garage was built  ",
    y= "Frequency",
    x="Year"
  )

summary(GarageYrBlt)
```


####12 -13 :GarageCars and GarageArea
 
GarageCars: Size of garage in car capacity

GarageArea: Size of garage in square feet


```{r gara ,echo=F}
ggplot(data,aes(x='', y=GarageArea))+ geom_boxplot(aes(fill=factor(GarageCars)),position="dodge" )+
  
  theme_bw() + theme( panel.grid.major = element_blank(), panel.grid.minor = element_blank())+
  labs(
    title="  Garage Area and GarageCars ",
    subtitle = "Color refer the number car",
    fill="",
    y= " Garage Area",
    x="Nummber of Cars in Garage"
  )
print("GarageArea")
summary(GarageArea )
print("GarageCars")
summary(GarageCars)

```


####14-22:WoodDeckSF , OpenPorchSF , EnclosedPorch , ThreeSsnPorch ,ScreenPorch 


####PoolArea,MasVnrArea,MasVnrArea , 1stFlrSF ,2ndFlrSF,



 WoodDeckSF: Wood deck area in square feet
 
 OpenPorchSF: Open porch area in square feet
 
 EnclosedPorch: Enclosed porch area in square feet
 
 ThreeSsnPorch: Three season porch area in square feet
 
 ScreenPorch: Screen porch area in square feet
 
 PoolArea: Pool area in square feet
 
 MasVnrArea: Masonry veneer area in square feet 
 
 1stFlrSF: First Floor square feet
 
 2ndFlrSF: Second floor square feet
 
```{r 14_22, echo=F, warning=FALSE}
wd<-ggplot(data,aes(WoodDeckSF))+ geom_density(fill ='maroon')+theme_bw() +
  theme( panel.grid.major = element_blank(), panel.grid.minor = element_blank())+
  labs(
    subtitle = "  Wood deck area \n in square feet ",
    title="WoodDeckSF",
    y= "",
    x="WoodDeckSF"
  )
opsf <-ggplot(data,aes(OpenPorchSF))+ geom_density(fill ='maroon')+theme_bw() +
  theme( panel.grid.major = element_blank(), panel.grid.minor = element_blank())+
  labs(
    subtitle = " Open porch area \n in square feet ",
    title="OpenPorchSF",
    y= "",
    x="OpenPorchSF"
  )


ep <-ggplot(data,aes(EnclosedPorch))+ geom_density(fill ='maroon')+theme_bw() +
  theme( panel.grid.major = element_blank(), panel.grid.minor = element_blank())+
  labs(
    subtitle = " Enclosed porch \n area in square feet ",
    title="EnclosedPorch",
    y= "",
    x="EnclosedPorch"
  )

tsp <- ggplot(data,aes(ThreeSsnPorch))+ geom_density(fill ='maroon')+theme_bw() +
  theme( panel.grid.major = element_blank(), panel.grid.minor = element_blank())+
  labs(
    subtitle = "  Three season \n porch area in square feet ",
    title=" ThreeSsnPorch",
    y= "",
    x="ThreeSsnPorch"
  )

sp <-ggplot(data,aes(ScreenPorch))+ geom_density(fill ='maroon')+theme_bw() +
  theme( panel.grid.major = element_blank(), panel.grid.minor = element_blank())+
  labs(
    subtitle = " Screen porch \n area in square feet ",
    title="ScreenPorch",
    y= "",
    x="ScreenPorch"
  )
pa<-ggplot(data,aes(PoolArea))+ geom_density(fill ='maroon')+theme_bw() +
  theme( panel.grid.major = element_blank(), panel.grid.minor = element_blank())+
  labs(
    subtitle = " Pool area in\n square feet ",
    title=" PoolArea ",
    y= "density",
    x="PoolArea"
  )


mva<- ggplot(data,aes(MasVnrArea)) + geom_density(fill="maroon")+
  theme_bw() +
  theme( panel.grid.major = element_blank(), panel.grid.minor = element_blank())+
  labs(
    title="  Masonry veneer area   ",
    subtitle = "",
    y= "",
    x="MasVnrArea"
  )


####
# 1stFlrSF: First Floor square feet
# 
# 2ndFlrSF: Second floor square feet


stfloor<-ggplot(data,aes(X1stFlrSF)) + geom_density(fill="maroon")+
  theme_bw() +
  theme( panel.grid.major = element_blank(), panel.grid.minor = element_blank())+
  labs(
    title=" First Floor area ",
    subtitle = " square feet  ",
    y= "",
    x="1st Floor area"
  )


ndfloor<-ggplot(data,aes(X2ndFlrSF)) + geom_density(fill="maroon")+
  theme_bw() +
  theme( panel.grid.major = element_blank(), panel.grid.minor = element_blank())+
  labs(
    title="  Second floor area",
    subtitle = " (square feet) ",
    y= "",
    x="Floor area"
  )

pushViewport(viewport(layout = grid.layout(3, 3)))

print(wd, vp = viewport(layout.pos.row = 1, layout.pos.col = 1))
print(opsf, vp = viewport(layout.pos.row = 1, layout.pos.col = 2))
print(ep, vp = viewport(layout.pos.row = 1, layout.pos.col = 3))
print(tsp, vp = viewport(layout.pos.row = 2, layout.pos.col = 1))
print(sp, vp = viewport(layout.pos.row = 2, layout.pos.col = 2))
print(pa, vp = viewport(layout.pos.row = 2, layout.pos.col = 3))
print(stfloor, vp = viewport(layout.pos.row = 3, layout.pos.col = 1))
print(ndfloor, vp = viewport(layout.pos.row = 3, layout.pos.col = 2))
print(mva, vp = viewport(layout.pos.row = 3, layout.pos.col = 3))


vars=cbind(WoodDeckSF,OpenPorchSF,EnclosedPorch,ThreeSsnPorch,ScreenPorch,PoolArea,X1stFlrSF,X2ndFlrSF,SalePrice)
pairs.panels(vars)# tạo ma trận tương quan
# corr.test(vars)
# print( corr.test(vars),short=FALSE)






#-----------------------------------------------------------------------------------


```
WoodDeckSF,OpenPorchSF,EnclosedPorch,ThreeSsnPorch,ScreenPorch,PoolArea,X1stFlrSF,X2ndFlrSF,
```
   WoodDeckSF      OpenPorchSF     EnclosedPorch    ThreeSsnPorch     ScreenPorch        PoolArea      
 Min.   :  0.00   Min.   :  0.00   Min.   :  0.00   Min.   :  0.00   Min.   :  0.00   Min.   :  0.000  
 1st Qu.:  0.00   1st Qu.:  0.00   1st Qu.:  0.00   1st Qu.:  0.00   1st Qu.:  0.00   1st Qu.:  0.000  
 Median :  0.00   Median : 25.00   Median :  0.00   Median :  0.00   Median :  0.00   Median :  0.000  
 Mean   : 94.24   Mean   : 46.66   Mean   : 21.95   Mean   :  3.41   Mean   : 15.06   Mean   :  2.759  
 3rd Qu.:168.00   3rd Qu.: 68.00   3rd Qu.:  0.00   3rd Qu.:  0.00   3rd Qu.:  0.00   3rd Qu.:  0.000  
 Max.   :857.00   Max.   :547.00   Max.   :552.00   Max.   :508.00   Max.   :480.00   Max.   :738.000  
    
                                                                                        
   X2ndFlrSF       X1stFlrSF
 Min.   :   0     Min.   : 334
 1st Qu.:   0     1st Qu.: 882  
 Median :   0     Median :1087  
 Mean   : 347     Mean   :1163          
 3rd Qu.: 728     3rd Qu.:1391               
 Max.   :2065     Max.   :4692     
                                                                                                       

```


The matix above is correlation matrix . 

1stFlrSF has the biggest value (0.61). x2ndFlrSF and Wooddesktop (0.32).  they  effect Sale price






#### 23-24-25-26:BsmtFinSF1 , BsmtFinType1,  BsmtFinSF2 and BsmtFinType2




BsmtFinSF1: Type 1 finished square feet  

BsmtFinType1: Rating of basement finished area 

BsmtFinSF2: Type 2 finished square feet ##

BsmtFinType2: Rating of basement finished area (if multiple types)




```{r bsmt,echo=F}



bfsf1<- ggplot(data,aes(BsmtFinSF1)) + geom_density(fill="maroon")+
  theme_bw() +
  theme( panel.grid.major = element_blank(), panel.grid.minor = element_blank())+
  labs(
    title="Type 1 finished\n  square feet",
    subtitle = " square feet ",
    y= "",
    x="area"
  )


bft1<-ggplot(data,aes(BsmtFinType1)) + geom_bar(fill="maroon")+
  theme_bw() +
  theme( panel.grid.major = element_blank(), panel.grid.minor = element_blank())+
  labs(
    title="Rating of basement \nfinished area  ",
    subtitle = " area type 1 ",
    y= "",
    x="Rates"
  )


# BsmtFinSF2: Type 2 finished square feet ##
# BsmtFinType2: Rating of basement finished area (if multiple types)


bfsf2<- ggplot(data,aes(BsmtFinSF2)) + geom_density(fill="maroon")+
  theme_bw() +
  theme( panel.grid.major = element_blank(), panel.grid.minor = element_blank())+
  labs(
    title="Type 2 finished\n  square feet",
    subtitle = " square feet ",
    y= "",
    x="area"
  )

bft2<-ggplot(data,aes(BsmtFinType2)) + geom_bar(fill="maroon")+
  theme_bw() +
  theme( panel.grid.major = element_blank(), panel.grid.minor = element_blank())+
  labs(
    title="Rating of basement \nfinished area  ",
    subtitle = " area type 1 ",
    y= "",
    x="Rates"
  )

pushViewport(viewport(layout = grid.layout(2, 2)))

print(bfsf1, vp = viewport(layout.pos.row = 1, layout.pos.col = 1))
print(bft1, vp = viewport(layout.pos.row = 1, layout.pos.col = 2))
print(bfsf2, vp = viewport(layout.pos.row = 2, layout.pos.col = 1))
print(bft2, vp = viewport(layout.pos.row = 2, layout.pos.col = 2))

print("Correlation matrix")
vars=cbind(BsmtFinSF1,BsmtFinSF2,BsmtFinType1,BsmtFinType2,SalePrice)
pairs.panels(vars)# tạo ma trận tương quan
# corr.test(vars)


```

```
    BsmtFinSF1       BsmtFinSF2            BsmtFinType1        BsmtFinType2    
  Min.   :   0.0   Min.   :   0.00         ALQ :220             ALQ :  19 
  1st Qu.:   0.0   1st Qu.:   0.00         BLQ :148             BLQ :  33 
  Median : 383.5   Median :   0.00         GLQ :418             GLQ :  14
  Mean   : 443.6   Mean   :  46.55         LwQ : 74             LwQ :  46
  3rd Qu.: 712.2   3rd Qu.:   0.00         Rec :133             Rec :  54 
   Max.   :5644.0   Max.   :1474.00        Unf :430             Unf :1256  
                                           NA's: 37             NA's:  38 
                 
```

#### LowQualFinSF ,GrLivArea,BsmtFullBath,BsmtHalfBath,BsmtFullBath,HalfBath


```{r remain , echo= F}
# LowQualFinSF: Low quality finished square feet (all floors)

lq <-ggplot(data,aes( LowQualFinSF ) ) + geom_density(fill="maroon")+
  theme_bw() +
  theme( panel.grid.major = element_blank(), panel.grid.minor = element_blank())
  

# 
# GrLivArea: Above grade (ground) living area square feet
# 

gl<-ggplot(data,aes( GrLivArea ) ) + geom_density(fill="maroon")+
  theme_bw() +
  theme( panel.grid.major = element_blank(), panel.grid.minor = element_blank())


# BsmtFullBath: Basement full bathrooms 
#
bfb<-ggplot(data,aes( BsmtFullBath ) ) + geom_bar(fill="maroon")+
  theme_bw() +
  theme( panel.grid.major = element_blank(), panel.grid.minor = element_blank())


# BsmtHalfBath: Basement half bathrooms
# 
bhb<-ggplot(data,aes( BsmtHalfBath ) ) + geom_bar(fill="maroon")+
  theme_bw() +
  theme( panel.grid.major = element_blank(), panel.grid.minor = element_blank())




# FullBath: Full bathrooms above grade
#
fb <- ggplot(data,aes( FullBath ) ) + geom_bar(fill="maroon")+
  theme_bw() +
  theme( panel.grid.major = element_blank(), panel.grid.minor = element_blank())




# HalfBath: Half baths above grade
# 

hb<-ggplot(data,aes( HalfBath ) ) + geom_bar(fill="maroon")+
  theme_bw() +
  theme( panel.grid.major = element_blank(), panel.grid.minor = element_blank())


# BedroomAbvGr: Bedrooms above grade (does NOT include basement bedrooms)
# 
ba<-ggplot(data,aes( BedroomAbvGr) ) + geom_bar(fill="maroon")+
  theme_bw() +
  theme( panel.grid.major = element_blank(), panel.grid.minor = element_blank())



# Kitchen: Kitchens above grade


ka<-ggplot(data,aes( KitchenAbvGr) ) + geom_bar(fill="maroon")+
  theme_bw() +
  theme( panel.grid.major = element_blank(), panel.grid.minor = element_blank())



# TotRmsAbvGrd: Total rooms above grade (does not include bathrooms)

tra<-ggplot(data,aes( TotRmsAbvGrd) ) + geom_bar(fill="maroon")+
  theme_bw() +
  theme( panel.grid.major = element_blank(), panel.grid.minor = element_blank())


# Fireplaces: Number of fireplaces
# 
fp<-ggplot(data,aes( Fireplaces) ) + geom_bar(fill="maroon")+
  theme_bw() +
  theme( panel.grid.major = element_blank(), panel.grid.minor = element_blank())


# BsmtUnfSF: Unfinished square feet of basement area
# 

bm<-ggplot(data,aes( BsmtUnfSF) ) + geom_density(fill="maroon")+
  theme_bw() +
  theme( panel.grid.major = element_blank(), panel.grid.minor = element_blank())

# TotalBsmtSF: Total square feet of basement area
tb<-ggplot(data,aes( TotalBsmtSF) ) + geom_density(fill="maroon")+
  theme_bw() +
  theme( panel.grid.major = element_blank(), panel.grid.minor = element_blank())


pushViewport(viewport(layout=grid.layout(2,3)))

print( lq , vp = viewport(layout.pos.row = 1, layout.pos.col = 1  ))
print( gl , vp = viewport(layout.pos.row = 1, layout.pos.col = 2  ))
print( bfb , vp = viewport(layout.pos.row = 1, layout.pos.col =3  ))
print( bhb , vp = viewport(layout.pos.row = 2, layout.pos.col =  1))
print( fb , vp = viewport(layout.pos.row = 2, layout.pos.col =  2))
print( hb , vp = viewport(layout.pos.row = 2, layout.pos.col =  3))

```




```{r remain2 ,echo=F  }

# BedroomAbvGr: Bedrooms above grade (does NOT include basement bedrooms)
# 
ba<-ggplot(data,aes( BedroomAbvGr) ) + geom_bar(fill="maroon")+
  theme_bw() +
  theme( panel.grid.major = element_blank(), panel.grid.minor = element_blank())



# Kitchen: Kitchens above grade


ka<-ggplot(data,aes( KitchenAbvGr) ) + geom_bar(fill="maroon")+
  theme_bw() +
  theme( panel.grid.major = element_blank(), panel.grid.minor = element_blank())



# TotRmsAbvGrd: Total rooms above grade (does not include bathrooms)

tra<-ggplot(data,aes( TotRmsAbvGrd) ) + geom_bar(fill="maroon")+
  theme_bw() +
  theme( panel.grid.major = element_blank(), panel.grid.minor = element_blank())


# Fireplaces: Number of fireplaces
# 
fp<-ggplot(data,aes( Fireplaces) ) + geom_bar(fill="maroon")+
  theme_bw() +
  theme( panel.grid.major = element_blank(), panel.grid.minor = element_blank())


# BsmtUnfSF: Unfinished square feet of basement area
# 

bm<-ggplot(data,aes( BsmtUnfSF) ) + geom_density(fill="maroon")+
  theme_bw() +
  theme( panel.grid.major = element_blank(), panel.grid.minor = element_blank())

# TotalBsmtSF: Total square feet of basement area
tb<-ggplot(data,aes( TotalBsmtSF) ) + geom_density(fill="maroon")+
  theme_bw() +
  theme( panel.grid.major = element_blank(), panel.grid.minor = element_blank())


pushViewport(viewport(layout=grid.layout(2,3)))


print( ba , vp = viewport(layout.pos.row = 1, layout.pos.col =  1))
print( ka , vp = viewport(layout.pos.row = 1, layout.pos.col =  2))
print( tra , vp = viewport(layout.pos.row = 1, layout.pos.col =  3))
print( fp , vp = viewport(layout.pos.row = 2, layout.pos.col =  1))
print( bm , vp = viewport(layout.pos.row = 2, layout.pos.col =  2))
print( tb , vp = viewport(layout.pos.row = 2, layout.pos.col =  3))


```


### Implement Linear model

```{r linearmodel , echo=F} 
set.seed(14) # chia radom dể test
ind <- sample(2, nrow(data), replace = TRUE, prob = c(0.7, 0.3))
train.data <- data [ind == 1, ]
test.data <- data[ind == 2, ]
md <- lm(SalePrice~. , data= train.data)
summary(md)
plot(md)



```

The Linear model can describle 89,27%. the change of sale price.




